---
title: 'Weighted Tables: JBCI Round 2 Cities'
author: "Connor Staggs"
date: "5/3/2023"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: united
  word_document:
    toc: yes
  pdf_document: default
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require('pacman')){install.packages('pacman')}
pacman::p_load(readxl, tidyverse, tidyr, janitor, survey, rockchalk, kableExtra, questionr, stringr, mgsub, flextable, writexl)
options(digits = 4)
```

```{r read_data, include = FALSE}
wd <- '/Users/cjs/Documents/Dropbox (Brown)/JBCI work'
setwd(wd)
# df <- read_csv('jbci_round_2_wts.csv') %>% clean_names()
# df <- read_csv('jbci_round_2_updated.csv') %>%  clean_names()

df <- read_csv('jbci_base_phase_3_june2023_wts_index_comps.csv') # updated data file from Siddharth
```

```{r functions, include = FALSE}
library(tidyverse)
library(tidyr)

crosstab_city <- function(df, q) {
  if (!all(c(q, 'city', 'weights') %in% colnames(df))) {
    stop('Not all column name(s) are present in dataframe.')
  }
  df %>% group_by_(df[["city"]], df[[q]]) %>% 
    summarise(wtd_n =sum(df[["weights"]])) %>% 
    group_by(df[["city"]]) %>% 
    mutate_(response = df[[q]],
           wtd_group_size = sum(wtd_n),
           proportion = wtd_n / wtd_group_size) %>% 
    select(df[["city"]], response, proportion) %>% 
    spread(response, proportion) %>% 
    relocate("DK", "RTA", .after = last_col())
}

# results <- list(A3 = a3,
#                 A4 = a4)
# write_xlsx(results, 'results.xlsx', col_names = TRUE)
```

```{r cleaning, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

### Clean and recode basic demographic variables

df <- df %>% 
  mutate(
    weights = ht_wt_s,
    city = qz1,
    ht = case_when(
      qz6 == 1 ~ 'HT1',
      qz6 == 2 ~ 'HT2',
      qz6 == 3 ~ 'HT3',
      qz6 == 4 ~ 'HT4',
      qz6 == 5 ~ 'HT5'
  ),
    rel = case_when(
      qe1 == 1 ~ 'Hindu',
      qe1 == 2 ~ 'Muslim',
      TRUE ~ 'Other',
  ),
    caste = case_when(
      qe2 == 1 ~ 'OBC',
      qe2 == 2 ~ 'SC',
      qe2 == 3 ~ 'ST',
      qe2 == 4 ~ 'Forward',
      TRUE ~ 'Other'
  ))

### E1: Religion
# 1: Hindu
# 2: Muslim
# 3: Christian
# 4: Jain
# 5: Sikh
# 6: Parsi
# 7: Buddhist
# 8: Neo-Buddhist
# 
# 9:Other (please specify)
# 88:Don’t Know
# 99:Refused to answer


### E2: Caste
# 1: OBC
# 2:SC
# 3:ST
# 4: General/Other / Forward Caste 
# 5: None of the above/Don't belong to a social group 
# 88: Don’t know 
# 99:Refused to answer

### Z6: housing type 
# 5: HT-5 (Upper Class) 
# 4: HT-4 (Upper Middle Class)
# 3: HT-3 (Lower Middle Class) 
# 2: HT-2 (Notified Slum) 
# 1: HT-1 (Self Built Housing/Shack)

### Z1: City Name
# 11: Kolkata
# 12: Delhi
# 13: Lucknow
# 14: Bhopal
# 15: Bhubaneswar
# 16: Ajmer
# 17: Jalandhar

```


## Section A: Citizenship

### A3: According to you, which of the following is the most important responsibility of a citizen of a democratic country such as India? (Single Entry)


```{r A3, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 1: Voting
# 2: Respecting the law
# 3: Treating others as equal 
# 4: Being involved in your community
# 
# 88: Don’t Know
# 99: Refused to answer

df <- df %>% 
  mutate(qa3 = case_when(
    qa3 == 1 ~ 'Voting',
    qa3 == 2 ~ 'Respecting the law',
    qa3 == 3 ~ 'Treating others as equal',
    qa3 == 4 ~ 'Being involved in your community',
    qa3 == 88 ~ 'DK',
    qa3 == 99 ~ 'RTA'
  ))

a3 <- df %>% 
  group_by(city, qa3) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa3,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a3, caption ='A3', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa3) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A3 (raw N)') %>%
  kable_styling(bootstrap_options = "hover")

### HT

a3_ht <- df %>% 
  group_by(city, ht, qa3) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qa3,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a3_ht, caption ='A4 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 


```
### A4: According to you, which of the following is the most important service provided by the government? (Single Entry)

```{r A4, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 1. WATER 
# 2. SANITATION
# 3. HEALTH SERVICES
# 4. EDUCATION
# 5. SAFETY AND PERSONAL SECURITY
# 6. CLEAN AIR
# 7. ELECTRICITY
# 8. PUBLIC TRANSPORTATION 
# 9. HOUSING
# 
# 88: Don’t Know 
# 99: Refused to answer

df <- df %>% 
  mutate(qa4 = case_when(
    qa4 == 1 ~ 'Water',
    qa4 == 2 ~ 'Sanitation',
    qa4 == 3 ~ 'Health Services',
    qa4 == 4 ~ 'Education',
    qa4 == 5 ~ 'Safety and Personal Security',
    qa4 == 6 ~ 'Clean Air',
    qa4 == 7 ~ 'Electricity',
    qa4 == 8 ~ 'Public Transportation',
    qa4 == 9 ~ 'Housing',
    qa4 == 88 ~ 'DK',
    qa4 == 99 ~ 'RTA'
  ))

a4 <- df %>% 
  group_by(city, qa4) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa4,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a4, caption ='A4', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa4) %>% 
        relocate('DK', 'RTA', .after = last_col())) %>%
  kable_styling(bootstrap_options = "hover") 


```
### A13: Do you know how to contact your ward corporator/councillor? (Single Entry)
```{r A13, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 0: No
# 1: Yes 
# 
# 88: Don’t Know
# 99: Refused to answer
df <- df %>% 
  mutate(qa13 = case_when(
    qa13 == 1 ~ 'Yes',
    qa13 == 0 ~ 'No',
    qa13 == 88 ~ 'DK',
    qa13 == 99 ~ 'RTA'
  ))

a13 <- df %>% 
  group_by(city, qa13) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa13,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a13, caption ='A13', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa13) %>% 
        relocate('DK', 'RTA', .after = last_col())) %>%
  kable_styling(bootstrap_options = "hover") 


```

### A19: Are you currently registered to vote in union/state elections? (Single Entry)

```{r A19, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 0: No, and I have not tried to register
# 1: No, but I have tried to register
# 2: Yes
# 88: Don’t Know
# 99: Refused to answer

df <- df %>% 
  mutate(qa19 = case_when(
    qa19 == 0 ~ 'No, and I have NOT tried to register',
    qa19 == 1 ~ 'No, but I HAVE tried to register',
    qa19 == 2 ~ 'Yes',
    qa19 == 88 ~ 'DK',
    qa19 == 99 ~ 'RTA'
  ))

a19 <- df %>% 
  group_by(city, qa19) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa19,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a19, caption ='A19', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa19) %>% 
        relocate('DK', 'RTA', .after = last_col())) %>%
  kable_styling(bootstrap_options = "hover") 


### HT
a19_ht <- df %>% 
  group_by(city, ht, qa19) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qa19,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a19_ht, caption ='A19 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```

### A20: Are you currently registered to vote in local/city/municipal elections? (Single Entry)

- Only have data for Bhubaneswar for this question, even though the questionnaire indicates it was to be asked in Lucknow and Bhopal as well.

```{r A20, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
### ASKED ONLY FOR BHOPAL, LUCKNOW, AND BHUBANESWAR (?)
# 0: No, and I have not tried to register
# 1: No, but I have tried to register
# 2: Yes
# 88: Don’t Know
# 99: Refused to answer

df <- df %>% 
  mutate(qa20 = case_when(
    qa20 == 0 ~ 'No, and I have NOT tried to register',
    qa20 == 1 ~ 'No, but I HAVE tried to register',
    qa20 == 2 ~ 'Yes',
    qa20 == 88 ~ 'DK',
    qa20 == 99 ~ 'RTA',
    TRUE ~ 'NA'
  ))

a20 <- df %>%  ## Add other cities later
  # filter(city %in% c('Lucknow', 'Bhopal', 'Bhubaneswar')) %>% 
  filter(city == 'Bhubaneswar') %>% 
  group_by(city, qa20) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa20,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())


kable(a20, caption ='A20', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa20) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A20 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 


### HT
a20_ht <- df %>% 
  # filter(city %in% c('Lucknow', 'Bhopal', 'Bhubaneswar')) %>% 
  filter(city == 'Bhubaneswar') %>% 
  group_by(city, ht, qa20) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qa20,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a20_ht, caption ='A20 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 


```


### A24: Which of these statements, in your opinion, describes your municipal corporator? (Single Entry)

```{r A24, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 1: He/ She cares about the wellbeing of all the people of their constituency
# 
# 2:He/ She cares only about the well-being of certain communities in their constituency
# 
# 3:He/ She is mostly is concerned with their own interests
# 
# 88: Don’t Know
# 99: Refused to answer

df <- df %>% 
  mutate(qa24 = case_when(
    qa24 == 1 ~ 'They care about the well-being of ALL the people of their constituency',
    qa24 == 2 ~ 'They care only about the well-being of CERTAIN communities in their constituency',
    qa24 == 3 ~ 'They are mostly concerned with their OWN interests',
    qa24 == 88 ~ 'DK',
    qa24 == 99 ~ 'RTA',
    TRUE ~ 'NA'
  ))

a24 <- df %>% 
  group_by(city, qa24) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa24,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a24, caption ='A24', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa24) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A24 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 


### HT

# a24_ht <- df %>% 
#   group_by(city, ht, qa24) %>%
#   summarise(wtd_n = sum(weights)) %>%
#   group_by(city, ht) %>%
#   mutate(response = qa24,
#          wtd_group_size = sum(wtd_n),
#          proportion = wtd_n / wtd_group_size) %>%
#   select(city, ht, response, proportion) %>% 
#   spread(response, proportion) %>%
#   relocate('DK', 'RTA', .after = last_col())
# 
# kable(a24_ht, caption ='A24 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 


```

### A25: Which of these statements, in your opinion, describes your current MLA? (Single Entry)

```{r A25, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 1: He/ She cares about the wellbeing of all the people of their constituency
# 2: He/ She cares only about the well-being of certain communities in their constit8uency
# 3: He/ She is mostly concerned with their own interests
# 88: Don’t Know
# 99: Refused to Answer

df <- df %>% 
  mutate(qa25 = case_when(
    qa25 == 1 ~ 'They care about the well-being of ALL the people of their constituency',
    qa25 == 2 ~ 'They care only about the well-being of CERTAIN communities in their constituency',
    qa25 == 3 ~ 'They are mostly concerned with their OWN interests',
    qa25 == 88 ~ 'DK',
    qa25 == 99 ~ 'RTA',
    TRUE ~ 'NA'
  ))

a25 <- df %>% 
  group_by(city, qa25) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa25,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a25, caption ='A25', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa25) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A25 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 


### HT

# a24_ht <- df %>% 
#   group_by(city, ht, qa24) %>%
#   summarise(wtd_n = sum(weights)) %>%
#   group_by(city, ht) %>%
#   mutate(response = qa24,
#          wtd_group_size = sum(wtd_n),
#          proportion = wtd_n / wtd_group_size) %>%
#   select(city, ht, response, proportion) %>% 
#   spread(response, proportion) %>%
#   relocate('DK', 'RTA', .after = last_col())
# 
# kable(a24_ht, caption ='A24 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 


```

### A26: Which of these statements, in your opinion, describes your current MP? (Single Entry)
```{r A26, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 1: He/ She cares about the wellbeing of all the people of their constituency
# 
# 2:He/ She cares only about the well-being of certain communities in their constituency
# 
# 3:He/ She is mostly is concerned with their own interests
# 
# 88: Don’t Know
# 99: Refused to answer
df <- df %>% 
  mutate(qa26 = case_when(
    qa26 == 1 ~ 'They care about the well-being of ALL the people of their constituency',
    qa26 == 2 ~ 'They care only about the well-being of CERTAIN communities in their constituency',
    qa26 == 3 ~ 'They are mostly concerned with their OWN interests',
    qa26 == 88 ~ 'DK',
    qa26 == 99 ~ 'RTA'
  ))

a26 <- df %>% 
  group_by(city, qa26) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa26,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a26, caption ='A26', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa26) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A26 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```


### A28: Compared with before the pandemic, has the perception of the following improved, deteriorated or remained the same? (Single Entry for each option)

```{r A28, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# A (1): Police
# B (2): Local Corporator
# C (3): MLA
# D (4): Local Leaders (un-elected)
# E (5): Government agencies
# G (6): NGOs
# H (7): Neighbours

### A28 is divided into several variables, as above.
### Response options for each are identical:

# 1: More positive
# 2: Feel the same way
# 3: Less positive
# 88: Don't know
# 99: Refused to answer 

df <- df %>% 
  mutate(
    qa28_a = case_when(
    qa28_a == 1 ~ 'More positive',
    qa28_a == 2 ~ 'Feel the same way',
    qa28_a == 3 ~ 'Less positive',
    qa28_a == 88 ~ 'DK',
    qa28_a == 99 ~ 'RTA'
  ),
  qa28_b = case_when(
    qa28_b == 1 ~ 'More positive',
    qa28_b == 2 ~ 'Feel the same way',
    qa28_b == 3 ~ 'Less positive',
    qa28_b == 88 ~ 'DK',
    qa28_b == 99 ~ 'RTA'
  ),
  qa28_c = case_when(
    qa28_c == 1 ~ 'More positive',
    qa28_c == 2 ~ 'Feel the same way',
    qa28_c == 3 ~ 'Less positive',
    qa28_c == 88 ~ 'DK',
    qa28_c == 99 ~ 'RTA'
  ),
  qa28_d = case_when(
    qa28_d == 1 ~ 'More positive',
    qa28_d == 2 ~ 'Feel the same way',
    qa28_d == 3 ~ 'Less positive',
    qa28_d == 88 ~ 'DK',
    qa28_d == 99 ~ 'RTA'
  ),
  qa28_e = case_when(
    qa28_e == 1 ~ 'More positive',
    qa28_e == 2 ~ 'Feel the same way',
    qa28_e == 3 ~ 'Less positive',
    qa28_e == 88 ~ 'DK',
    qa28_e == 99 ~ 'RTA'
  ),
  qa28_g = case_when(
    qa28_g == 1 ~ 'More positive',
    qa28_g == 2 ~ 'Feel the same way',
    qa28_g == 3 ~ 'Less positive',
    qa28_g == 88 ~ 'DK',
    qa28_g == 99 ~ 'RTA'
  ),
  qa28_h = case_when(
    qa28_h == 1 ~ 'More positive',
    qa28_h == 2 ~ 'Feel the same way',
    qa28_h == 3 ~ 'Less positive',
    qa28_h == 88 ~ 'DK',
    qa28_h == 99 ~ 'RTA'
  )
)

```

#### A28a: Police

```{r A28a, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
a28a <- df %>% 
  group_by(city, qa28_a) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa28_a,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a28a, caption ='A28 (Police)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa28_a) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A28a (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```

#### A28b: Local Corporator

```{r A28b, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
a28b <- df %>% 
  group_by(city, qa28_b) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa28_b,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a28b, caption ='A28 (Local Corporator)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa28_b) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A28b (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```

#### A28c: MLA
```{r A28c, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
a28c <- df %>% 
  group_by(city, qa28_c) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa28_c,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a28c, caption ='A28c (MLA)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa28_c) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A28c (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```
#### A28d: Local Leaders (un-elected)
```{r A28d, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
a28d <- df %>% 
  group_by(city, qa28_d) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa28_d,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a28d, caption ='A28d (Local Leaders)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa28_d) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A28d (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```
#### A28e: Government Agencies
```{r A28e, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
a28e <- df %>% 
  group_by(city, qa28_e) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa28_e,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a28e, caption ='A28e (Government Agencies)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa28_e) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A28e (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```
#### A28g: NGOs
```{r A28g, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
a28g <- df %>% 
  group_by(city, qa28_g) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa28_g,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a28g, caption ='A28g (NGOs)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa28_g) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A28g (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```
#### A28h: Neighbours
```{r A28h, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
a28h <- df %>% 
  group_by(city, qa28_h) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa28_h,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a28h, caption ='A28h (Neighbours)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa28_h) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A28h (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```
### A33: Who do you think is most important in ensuring that your neighborhood receives public services from the provider?
```{r A33, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 1. MLA 
# 2. MP. 
# 3. Corporator
# 4. Local Political Leader (Unelected)
# 5. Middleman/Intermediary
# 6. The Government office responsible for the service (and the people who work there)
# 7. Other person of Influence
# 
# 88: Don’t Know
# 99: Refused to answer

df <- df %>% 
  mutate(qa33 = case_when(
    qa33 == 1 ~ 'MLA',
    qa33 == 2 ~ 'MP',
    qa33 == 3 ~ 'Corporator',
    qa33 == 4 ~ 'Local Political Leader (unelected)',
    qa33 == 5 ~ 'Middleman/Intermediary',
    qa33 == 6 ~ 'The government office responsible for that service (and the workers there)',
    qa33 == 7 ~ 'Other person of influence',
    qa33 == 88 ~ 'DK',
    qa33 == 99 ~ 'RTA'
  ))

a33 <- df %>% 
  group_by(city, qa33) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa33,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a33, caption ='A33', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa33) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A33 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

### HT 
a33_ht <- df %>% 
  group_by(city, ht, qa33) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qa33,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a33_ht, caption ='A33 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```
### A34: Are you aware of a ward committee in your neighbourhood where local issues are discussed? (Not informal neighbourhood committees)
```{r A34, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 0:No
# 1:Yes 
# 88:Don’t Know
# 99: Refused to answer
df <- df %>% 
  mutate(qa34 = case_when(
    qa34 == 0 ~ 'No',
    qa34 == 1 ~ 'Yes',
    qa34 == 88 ~ 'DK',
    qa34 == 99 ~ 'RTA'
  ))

a34 <- df %>% 
  group_by(city, qa34) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa34,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a34, caption ='A34', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qa34) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A34 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

### HT 
a34_ht <- df %>% 
  group_by(city, ht, qa34) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qa34,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a34_ht, caption ='A34 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```
### A34a: If yes, in the last year, did you, or someone in your household, attend ward committee meetings? (Responses only tabulated for those who answered 'Yes' to A34)
```{r A34a, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 0:No
# 1:Yes 
# 88:Don’t Know
# 99: Refused to answer

a34a_df <- df %>% # just filters for those who answered A34.
  filter(!is.na(qa34a)) %>% 
  mutate(qa34a = case_when(
    qa34a == 0 ~ 'No',
    qa34a == 1 ~ 'Yes',
    qa34a == 88 ~ 'DK',
    qa34a == 99 ~ 'RTA'
  ))

a34a <- a34a_df %>% 
  group_by(city, qa34a) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qa34a,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a34a, caption ='A34a', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(a34a_df, city, qa34a) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'A34a (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 


### HT 
a34a_ht <- a34a_df %>% 
  group_by(city, ht, qa34a) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qa34a,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(a34a_ht, caption ='A34a (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```


## Section B: Services

### B1: What is the main source of water for members of your household? (Single Entry) Check one option only (Only main source).

```{r B1, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 1. Tap (Piped)
# 2. Well (Covered or Uncovered)
# 3. Hand pump
# 4. Borewell
# 5. Other source (Record other source)
# 
# 88: Don't know
# 99: Refused to Answer

df <- df %>% 
  mutate(qb1 = case_when(
    qb1 == 1 ~ 'Tap (Piped)',
    qb1 == 2 ~ 'Well (Covered or Uncovered)',
    qb1 == 3 ~ 'Hand pump',
    qb1 == 4 ~ 'Borewell',
    qb1 == 5 ~ 'Other source (Record other source)',
    qb1 == 88 ~ 'DK',
    qb1 == 99 ~ 'RTA'
  ))

b1 <- df %>% 
  group_by(city, qb1) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qb1,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b1, caption ='B1', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qb1) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'B1 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

### HT 
b1_ht <- df %>% 
  group_by(city, ht, qb1) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qb1,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b1_ht, caption ='B1 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```

### B11: Does the house have electricity? (Single Entry)

```{r B11, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 0: No
# 1: Yes  
# 88: Don’t Know
# 99: Refused to answer

df <- df %>% 
  mutate(qb11 = case_when(
    qb11 == 0 ~ 'No',
    qb11 == 1 ~ 'Yes',
    qb11 == 88 ~ 'DK',
    qb11 == 99 ~ 'RTA'
  ))

b11 <- df %>% 
  group_by(city, qb11) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qb11,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b11, caption ='B11', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qb11) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'B11 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

### HT 
b11_ht <- df %>% 
  group_by(city, ht, qb11) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qb11,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b11_ht, caption ='B11 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```

### B11a: Is the electricity metered? (Single Entry) *Only for those who answered 'yes' to B11.*

```{r B11a, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# sum(is.na(df$qb11a))

# 0: No
# 1: Yes  
# 88: Don’t Know
# 99: Refused to answer

b11a_df <- df %>% # just filters for those who answered B11 'yes'.
  filter(!is.na(qb11a)) %>% 
  mutate(qb11a = case_when(
    qb11a == 0 ~ 'No',
    qb11a == 1 ~ 'Yes',
    qb11a == 88 ~ 'DK',
    qb11a == 99 ~ 'RTA'
  ))

b11a <- b11a_df %>% 
  group_by(city, qb11a) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qb11a,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b11a, caption ='B11a', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(b11a_df, city, qb11a) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'B11a (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

### HT 
b11a_ht <- b11a_df %>% 
  group_by(city, ht, qb11a) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qb11a,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b11a_ht, caption ='B11a (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```

### B12: What kind of toilet facility does the household have? (Single Entry)
```{r B12, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 1. Flush/Pour Flush Latrine within premises connected to a Piped Sewer System
# 2. Flush/Pour Flush Latrine within premises connected to Septic Tank 
# 3. Flush/Pour Flush Latrine within premises connected to any Other System (not connected to a sewer line): Open drainage into ground or into water body through covered drain or uncovered drain.
# 4. Pit Latrine: Ventilated or Covered Pit
# 5: Pit Latrine: Open Pit
# 6.No Latrine within Premises: Public Latrine
# 7: No Latrine within Premises: Open Defecation
# 98: Other (please specify)
# 88: Don’t Know
# 99: Refused to answer

df <- df %>% 
  mutate(qb12 = case_when(
    qb12 == 1 ~ 'Piped Sewer',
    qb12 == 2 ~ 'Septic Tank',
    qb12 == 3 ~ 'Open Drainage',
    qb12 == 4 ~ 'Ventilated/Covered Pit',
    qb12 == 5 ~ 'Open Pit',
    qb12 == 6 ~ 'Public Latrine',
    qb12 == 7 ~ 'Open Defecation',
    qb12 == 98 ~ 'Other (please specify)',
    qb12 == 88 ~ 'DK',
    qb12 == 99 ~ 'RTA'))

b12 <- df %>% 
  group_by(city, qb12) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qb12,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b12, caption ='B12', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qb12) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'B12 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

### HT 
b12_ht <- df %>% 
  group_by(city, ht, qb12) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qb12,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b12_ht, caption ='B12 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```

### B14: What is the type of road in front of your house? (Single Entry)
```{r B14, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 1:Pakka
# 2:Kutcha 
# 88:Don’t Know 
# 99:Refused to answer

df <- df %>% 
  mutate(qb14 = case_when(
    qb14 == 1 ~ 'Pakka',
    qb14 == 2 ~ 'Kutcha',
    qb14 == 88 ~ 'DK',
    qb14 == 99 ~ 'RTA'))

b14 <- df %>% 
  group_by(city, qb14) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qb14,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b14, caption ='B14', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qb14) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'B14 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

### HT 
b14_ht <- df %>% 
  group_by(city, ht, qb14) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qb14,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b14_ht, caption ='B14 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```

### B16: Does the road in front of your house get water-logged during monsoon? (Single Entry)
```{r B16, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 0: No
# 1: Yes 
# 88:Don’t Know 
# 99:Refused to answer

df <- df %>% 
  mutate(qb16 = case_when(
    qb16 == 0 ~ 'No',
    qb16 == 1 ~ 'Yes',
    qb16 == 88 ~ 'DK',
    qb16 == 99 ~ 'RTA'))

b16 <- df %>% 
  group_by(city, qb16) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qb16,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b16, caption ='B16', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qb16) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'B16 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

### HT 
b16_ht <- df %>% 
  group_by(city, ht, qb16) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city, ht) %>%
  mutate(response = qb16,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, ht, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(b16_ht, caption ='B16 (HT)', digits = 4) %>% kable_styling(bootstrap_options = "hover") 
```

## Section C: Experiences Accessing Government Offices

### C1: In the past six months how many times did you visit/contact your Municipal Corporator/ward corporator for any service related issue? (Single Entry)
- *These options had zero entries: 14, 16-19, 21-25.*
```{r C1, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# Drop down for the number of visits "0 to 25"
# 26th Option: More than 25
# 88: Don’t Know 
# 99: Refused to answer

## In reality, numbers range from from 0 - 15, no 14, nothing between 16-25.
df <- df %>%
  mutate(qc1 = case_when(
    qc1 == 88 ~ "DK",
    qc1 == 99 ~ "RTA",
    qc1 <= 25 ~ as.character(qc1),
    TRUE ~ "More than 25"
  )) %>% 
    mutate(qc1 = factor(qc1, levels = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "15", "20", "More than 25", "DK", "RTA"), ordered = TRUE))
 
c1 <- df %>% 
  group_by(city, qc1) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qc1,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(c1, caption ='C1', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qc1) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'C1 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```


## Section D: Discrimination

### D11:According to you, IN THIS CITY, does unfair treatment ever  occur on the basis of Caste? (Single Entry) 
```{r D11, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 0: No
# 1: Yes 
# 88:Don’t Know 
# 99:Refused to answer

df <- df %>% 
  mutate(qd11 = case_when(
    qd11 == 0 ~ 'No',
    qd11 == 1 ~ 'Yes',
    qd11 == 88 ~ 'DK',
    qd11 == 99 ~ 'RTA'))

d11 <- df %>% 
  group_by(city, qd11) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qd11,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(d11, caption ='D11', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qd11) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'D11 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```
### D12: According to you, IN THIS CITY, does unfair treatment ever  occur on the basis of Religion? (Single Entry) 
```{r D12, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 0: No
# 1: Yes 
# 88:Don’t Know 
# 99:Refused to answer

df <- df %>% 
  mutate(qd12 = case_when(
    qd12 == 0 ~ 'No',
    qd12 == 1 ~ 'Yes',
    qd12 == 88 ~ 'DK',
    qd12 == 99 ~ 'RTA'))

d12 <- df %>% 
  group_by(city, qd12) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qd12,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(d12, caption ='D12', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qd12) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'D12 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```

### D13: According to you, IN THIS CITY, does unfair treatment ever  occur on the basis of Gender? (Single Entry) 
```{r D13, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 0: No
# 1: Yes 
# 88:Don’t Know 
# 99:Refused to answer

df <- df %>% 
  mutate(qd13 = case_when(
    qd13 == 0 ~ 'No',
    qd13 == 1 ~ 'Yes',
    qd13 == 88 ~ 'DK',
    qd13 == 99 ~ 'RTA'))

d13 <- df %>% 
  group_by(city, qd13) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qd13,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(d13, caption ='D13', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qd13) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'D13 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```

### D22: According to your perception, how was your caste /community treated during the pandemic? (Single Entry)
```{r D22, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 1: Fairly
# 2: Unfairly
# 88: Don't know
# 99: Refused to answer

df <- df %>% 
  mutate(qd22 = case_when(
    qd22 == 1 ~ 'Fairly',
    qd22 == 2 ~ 'Unfairly',
    qd22 == 88 ~ 'DK',
    qd22 == 99 ~ 'RTA'))

d22 <- df %>% 
  group_by(city, qd22) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qd22,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(d22, caption ='D22', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qd22) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'D22 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```

### D23: According to your perception, how was your religious community treated during the pandemic? (Single Entry)
```{r D23, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 1: Fairly
# 2: Unfairly
# 88: Don't know
# 99: Refused to answer

df <- df %>% 
  mutate(qd23 = case_when(
    qd23 == 1 ~ 'Fairly',
    qd23 == 2 ~ 'Unfairly',
    qd23 == 88 ~ 'DK',
    qd23 == 99 ~ 'RTA'))

d23 <- df %>% 
  group_by(city, qd23) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qd23,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('DK', 'RTA', .after = last_col())

kable(d23, caption ='D23', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qd23) %>% 
        relocate('DK', 'RTA', .after = last_col()),
      caption = 'D23 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```

## Section E

### E1: Which religion do you follow?
```{r E1, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
## Re-load data so that categories are not collapsed into 'Other'
df <- read_csv('jbci_round_2_wts.csv') %>% 
  clean_names() %>% 
  mutate(
    weights = ht_wt_s,
    city = qz1,
    ht = case_when(
      qz6 == 1 ~ 'HT1',
      qz6 == 2 ~ 'HT2',
      qz6 == 3 ~ 'HT3',
      qz6 == 4 ~ 'HT4',
      qz6 == 5 ~ 'HT5'
  ),
)

# 1: Hindu
# 2: Muslim
# 3: Christian
# 4: Jain
# 5: Sikh
# 6: Parsi
# 7: Buddhist
# 8: Neo-Buddhist
# 
# 9:Other (please specify)
# 88:Don’t Know
# 99:Refused to answer

df <- df %>% 
  mutate(qe1 = case_when(
    qe1 == 1 ~ 'Hindu',
    qe1 == 2 ~ 'Muslim',
    qe1 == 3 ~ 'Christian',
    qe1 == 4 ~ 'Jain',
    qe1 == 5 ~ 'Sikh',
    qe1 == 6 ~ 'Parsi',
    qe1 == 7 ~ 'Buddhist',
    qe1 == 8 ~ 'Neo-Buddhist',
    qe1 == 9 ~ 'Other (please specify)',
    qe1 == 88 ~ 'DK',
    qe1 == 99 ~ 'RTA',
    TRUE ~ 'NA'
  ))

e1 <- df %>%  
  group_by(city, qe1) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qe1,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>%
  relocate('Sikh', 'Christian', 'Buddhist', 'Jain', 'Parsi', 'Other (please specify)','DK', 'RTA', .after = last_col())


kable(e1, caption ='E1', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qe1) %>% 
        relocate('Sikh', 'Christian', 'Buddhist', 'Jain', 'Parsi', 'Other (please specify)', 'DK', 'RTA', .after = last_col()),
      caption = 'E1 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 


```
### E2: Which social group (caste) do you belong to?
```{r E2, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
df <- df %>% 
  mutate(caste = case_when(
      qe2 == 1 ~ 'OBC',
      qe2 == 2 ~ 'SC',
      qe2 == 3 ~ 'ST',
      qe2 == 4 ~ 'Forward',
      qe2 == 5 ~ 'None of the above/no caste',
      qe2 == 88 ~ 'DK',
      qe2 == 99 ~ 'RTA'
  ))

e2 <- df %>%  
  group_by(city, caste) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = caste,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) %>% 
  relocate('None of the above/no caste', 'DK', 'RTA', .after = last_col())


kable(e2, caption ='E2', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, caste) %>% 
        relocate('None of the above/no caste', 'DK', 'RTA', .after = last_col()),
      caption = 'E2 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 

df <- read_csv('jbci_round_2_wts.csv') %>%
  clean_names() %>% 
  mutate(
    weights = ht_wt_s,
    city = qz1,
    ht = case_when(
      qz6 == 1 ~ 'HT1',
      qz6 == 2 ~ 'HT2',
      qz6 == 3 ~ 'HT3',
      qz6 == 4 ~ 'HT4',
      qz6 == 5 ~ 'HT5'
  ),
    rel = case_when(
      qe1 == 1 ~ 'Hindu',
      qe1 == 2 ~ 'Muslim',
      TRUE ~ 'Other',
  ),
    caste = case_when(
      qe2 == 1 ~ 'OBC',
      qe2 == 2 ~ 'SC',
      qe2 == 3 ~ 'ST',
      qe2 == 4 ~ 'Forward',
      TRUE ~ 'Other'
  ))


```

## Section F

### F1: Till what level have you studied?
```{r F1, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}

# 1: No Schooling/Illiterate
# 2: Literate but no formal schooling
# 3: School- up to 4 years
# 4: School- 5-9 years
# 5: School- SSC/HSC
# 6: Some college but not graduated
# 7: College Graduate: General
# 8: College Graduate: Professional
# 9: Post-Graduate: General
# 10: Post-Graduate: Professional 
# 
# 88: Don’t Know
# 99: Refused to answer

df <- df %>% 
  mutate(qf1 = case_when(
    qf1 == 1 ~ 'No Schooling/illiterate',
    qf1 == 2 ~ 'Literate but no formal schooling',
    qf1 == 3 ~ 'School: up to 4 years',
    qf1 == 4 ~ 'School: 5-9 years',
    qf1 == 5 ~ 'School: SSC/HSC',
    qf1 == 6 ~ 'Some college but not graduated',
    qf1 == 7 ~ 'College Graduate: General',
    qf1 == 8 ~ 'College Graduate: Professional',
    qf1 == 9 ~ 'Post-Graduate: General',
    qf1 == 10 ~ 'Post-Graduate: Professional',
    qf1 == 88 ~ 'DK',
    qf1 == 99 ~ 'RTA')) %>% 
  mutate(qf1 = factor(qf1, 
                      levels = c(
                        "No Schooling/illiterate", 
                        "Literate but no formal schooling", 
                        "School: up to 4 years", 
                        "School: 5-9 years", 
                        "School: SSC/HSC", 
                        "Some college but not graduated", 
                        "College Graduate: General", 
                        "College Graduate: Professional", 
                        "Post-Graduate: General", 
                        "Post-Graduate: Professional", 
                        "DK", 
                        "RTA"), 
                      ordered = TRUE))

f1 <- df %>% 
  group_by(city, qf1) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qf1,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) #%>%
  #relocate('DK', 'RTA', .after = last_col())

kable(f1, caption ='F1', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qf1),
      caption = 'F1 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 
```

## Section Z
### Z12: Gender of the respondent
```{r Z12, echo = FALSE, message=FALSE, cache = TRUE, results = 'asis'}
# 1: Female
# 2: Male
# 3: Other

df <- df %>% # just filters for those who answered A34.
  mutate(qz12 = case_when(
    qz12 == 1 ~ 'Female',
    qz12 == 2 ~ 'Male',
    qz12 == 3 ~ 'Other',
  ))

z12 <- df %>% 
  group_by(city, qz12) %>%
  summarise(wtd_n = sum(weights)) %>%
  group_by(city) %>%
  mutate(response = qz12,
         wtd_group_size = sum(wtd_n),
         proportion = wtd_n / wtd_group_size) %>%
  select(city, response, proportion) %>% 
  spread(response, proportion) 

kable(z12, caption ='Z12', digits = 4) %>% kable_styling(bootstrap_options = "hover") 

kable(tabyl(df, city, qz12),
      caption = 'Z12 (raw N)') %>%
  kable_styling(bootstrap_options = "hover") 


```